Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-01-11 ms.tex
I merged all of Adam's edits into the main ms.tex file.

The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}
whose surface and vertical structure may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}), and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}). Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), and virtually all L dwarfs and most T dwarfs likely have photospheric heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}. Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).

Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity. The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been show to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}). Wavelength-dependent phase variance in lightcurves has also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}. Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsation \citep{2014ApJ...785..158R}.

Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
Some ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) have been limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient calibrators \citep{2003MNRAS.339..477B}.
In contrast, the stability of space-based platforms $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision, and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}. However, these facilities are not suited, for building up robust statistical samples to assess the physical bases of surface heterogeneity or different variability modes.

Multi-Object Spectroscopy (MOS) which uses references stars to correct for telluric effects with a multi-object spectrograph or long slit \citep[e.g.][]{bean10,bean2013,gibson13clouds,stevenson2016hatp26} has significantly improved the precision of ground-based spectro-photometry. \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit. This was sufficient to infer the presence of a cloud/haze layer in Corot-1b via transmission spectroscopy. A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}. In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion. These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground and with IRTF from 1-2.5~$\mu$m.

This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions. We describe the target identification strategy and pilot targets in Section~\ref{sec:targets}.
In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
In Section~\ref{sec:ModelFits}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
We summarize our results in Section~\ref{sec:conclusions}.

\section{Target Selection}\label{sec:targets}

We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}. The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$. We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.  Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been observed to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}. Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming radius R = 1~{\rjup}. There is an $H$ = 12.3 star (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}). 
2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G}. This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.  \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths. There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 29$\arcsec$ separation; we chose the latter for our monitoring observations.

\begin{deluxetable*}{llcccccccl}
\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
\tablewidth{0pt}
\tablehead{
\colhead{Name} & 
\colhead{SpT} & 
\colhead{$d$} & 
\colhead{2MASS $H$} & 
\colhead{$J-K_s$} & 
\colhead{\teff} & 
\colhead{P$_{rot}$} &
\colhead{$v\sin{i}$} & 
\colhead{$i$\tablenotemark{a}} & 
\colhead{Refs} \\
 &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($degree$)} \\
 }
\startdata
{\sha} & L5 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
{\shb} & L4.5pec & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1600$\pm$100 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
\enddata
\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.2$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s. A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
\tablenotetext{b}{Tentative period.}
\tablerefs{(1) \citet{2003AJ....126.2421C};
(2) \citet{2012ApJ...752...56F}; 
(3) \citet{2015ApJ...810..158F};
(4) \citet{2004MNRAS.354..378K};
(5) \citet{2010ApJ...723..684B};
(6) \citet{2008ApJ...686..528L}; 
(7) \citet{2016MNRAS.455..357S};
(8) \citet{2015ApJ...798...73G};
(9) \citet{2015ApJ...799..154M}
(10) \citet{2015ApJ...798L..13Y}; 
}
\end{deluxetable*}

@@

We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. The short-wavelength limit was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
For {\sha} our exposures were 15~sec, which was sufficient for guiding but not precision photometry. For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.

\begin{deluxetable*}{lcccccccll}
\tablecaption{Observations}\label{tab:obsParam}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{3}{c}{Observation Epoch (UT)} \\
 \cline{2-4}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{End} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM} \\
 & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 352 & 60 & 7.47 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 363 & 45 & 4.65 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including the reset times and overheads. The FWHM is the measured median value of the time series around 1.6$\mu$m.}
\end{deluxetable*}

Wavelength calibrations were performed using observations of ThAr  emission lamps with the 0.3$\times$60$\arcsec$.
We also obtained calibration sequences of ThAr and flat-field lamps with the 3$\times$60$\arcsec$ slit  before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.

[ADAM STOPPED HERE]

For 2MASS J0835, we use a combination of an incandescent lamp and a sky frame to construct a flat.
Due to flexure and motion with thin the system, we use a sky frame to get the structure of the background with low order polynomials fits in the horizontal direction.
All of the (large $\gtrsim$ 30 px) structure is removed from the lamp frame with low order polynomials, and this residual flat is used to correct the pixel-to-pixel variations while the sky frame is used to measure the larger structures.
We cross-correlate the sky frame with each image to account for any spatial shifts and apply the pixel-to-pixel flat to construct a custom flat field for every image.

For 2MASS J1821, we did not have sufficient sky frames for sky flats so we use an incandescent lamp for flat fielding.
Here, we fit the flat field structure with low order polynomials in the incandescent flat field to describe the spatial structure and use the residual image as a pixel-to-pixel flat.
As in 2MASS J0835, we cross-correlate the spatial structure image to find a shift and then multiply it by the pixel-to-pixel flat to create a custom flat field for every image.
In both 2MASS J0835 and 2MASS J1821 we remove all spectral structure from the flat fields to make ``response'' images that do not include the spectral structure of the lamp or dramatically alter the flux levels that would affect SNR calculations from the number of photo-electrons in a given pixel.

As in \citet{2016ApJ...826..156S}, we perform background subtraction over the entire slit with polynomial fit.
We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.
We use optimal extraction \citep{horne1986optimalE} to maximize the signal to noise.
The spatial profiles are fit with low order polynomials with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
These spatial profiles are then used to calculate a weighted sum spectrum.

@@

Figure \ref{fig:specphot} shows the dynamic spectra of both targets, as well as the median spectra of the target and reference stars.
{\sha} shows no variations or systematics at the $\lesssim1$\% level, while {\shb} shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths. The periodic signal is coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than arising from systematic effects (see \citealt{2016ApJ...826..156S}).
{\shb} does exhibits some systematic features near the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by slight wavelength drifts and lower signals-to-noise.

@@

\section{Sinusoidal Model Fits}\label{sec:ModelFits}

We extracted separate light curves for each target in 25 spectral bins of width 0.060~$\mu$m, as shown in Figure~\ref{fig:tserPfold}. Each of these were fit to a simple sinusoidal model:
\begin{equation}\label{eq:cosfit}
F(t) = A \cos(2 \pi (t - t_0)/\tau) + B t + C
\end{equation}
Here, $F(t)$ is the flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters, but fixed $\tau$ at the literature value of rotation period due to systematic trends (with a period of $\sim$24 hr) caused by uncorrected telluric variations.
We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.

>>>>

The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}
whose surface and vertical structure may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}), and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}). Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), and virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}. Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).

Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity. The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been shown to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}). Wavelength-dependent phase variance in lightcurves has also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}. Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsation \citep{2014ApJ...785..158R}.

Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient calibrators \citep{2003MNRAS.339..477B}.
In contrast, the stability of space-based platforms such as $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision, and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}. However, these facilities are poorly suited for building up robust statistical samples to assess the physical origins of surface heterogeneity, or evolution in variability modes.

Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which references stars are simultaneously observed to correct for telluric effects  (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}) can significantly improve the precision of ground-based spectro-photometry. \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit. This was sufficient to infer the presence of a cloud/haze layer in Corot-1b via transmission spectroscopy. A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}. In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion. These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.

This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions. We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
In Section~\ref{sec:ModelFits}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
We summarize our results in Section~\ref{sec:conclusions}.

\section{Target Selection and Characterization}\label{sec:targets}

We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}. The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$. We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.  Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}. Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}. There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}). 
2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G}. This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.  \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths. There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 29$\arcsec$ separation; we chose the latter for our monitoring observations.

\begin{deluxetable*}{llcccccccl}
\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
\tablewidth{0pt}
\tablehead{
\colhead{Name} & 
\colhead{SpT} & 
\colhead{$d$} & 
\colhead{2MASS $H$} & 
\colhead{$J-K_s$} & 
\colhead{\teff} & 
\colhead{P$_{rot}$} &
\colhead{$v\sin{i}$} & 
\colhead{$i$\tablenotemark{a}} & 
\colhead{Refs} \\
 &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($degree$)} \\
 }
\startdata
2MASS~J08354256$-$0819237 & L5 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
2MASS~J18212815+14140101 & L4.5pec & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1600$\pm$100 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
\enddata
\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.2$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s. A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
\tablenotetext{b}{Tentative period.}
\tablerefs{(1) \citet{2003AJ....126.2421C};
(2) \citet{2012ApJ...752...56F}; 
(3) \citet{2015ApJ...810..158F};
(4) \citet{2004MNRAS.354..378K};
(5) \citet{2010ApJ...723..684B};
(6) \citet{2008ApJ...686..528L}; 
(7) \citet{2016MNRAS.455..357S};
(8) \citet{2015ApJ...798...73G};
(9) \citet{2015ApJ...799..154M}
(10) \citet{2015ApJ...798L..13Y}; 
}
\end{deluxetable*}

@@

We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. 
Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis. This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differental color refraction. The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50. Integration times were 60~s and 45~s for {\sha} and {\shb}, respectively. The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry. For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.

\begin{deluxetable*}{lccccccccc}
\tablecaption{Observations}\label{tab:obsParam}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{3}{c}{Observation Epoch (UT)} \\
 \cline{2-4}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{End} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM \@ $H$} \\
 & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 352 & 60 & 7.47 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 363 & 45 & 4.65 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including the reset times and overheads. The FWHM is the measured median value of the time series around 1.6$\mu$m.}
\end{deluxetable*}

Wavelength calibrations were performed using observations of ThAr emission lamps with the 0$\farcs$3$\times$60$\arcsec$.
We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.
% to measure pixel response and assess flexure in the instrument with telescope orientation.
For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response. 
To correct for instrument flexure, we also cross-correlated the sky frame with each science image to measure spatial shifts {\bf [WHAT ORDER OF SHIFT DID YOU FIND]}. These shifts were used to apply a custom flat field for every image.
For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis. {\bf [IS THIS TRUE FOR 1821?]}

As described in \citet{2016ApJ...826..156S}, we performed spatial background subtraction over the entire slit using a 4th-order polynomial fit to points more than 30 pixels away from the center of the source dispersion traces.  Spectra were optimally extracted \citep{1986ApJ...302..757H}, with spatial profiles fit to low order polynomials {\bf [REALLY? NOT A MEDIAN PROFILE? OR A MODIFIED GAUSSIAN? LOW ORDER POLY WOULDN'T CAPTURE PSF SHAPE I THINK]} with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
These spatial profiles were then used to calculate a weighted sum spectrum across the illuminated detector for each source and exposure. 
Typical signals-to-noise of the extracted spectra were {\bf [WHAT?]}. 
Relative spectra (source/reference) were then computed for each exposure. {\bf [DID YOU HAVE TO TAKE INTO ACCOUNT RELATIVE WAVELENGTH SHIFTS BETWEEN SOURCE AND REFERENCE STAR? I DON'T THINK DISPERSION IS STRICTLY ALIGNED WITH PIXEL AXES AND MAY HAVE SOME CURVATURE]}.

{\bf [MORIS REDUCTION FOR 1821?]}

\section{Analysis}

@@

Figure \ref{fig:specphot} shows the dynamic spectra (relative source brightness as a function of wavelength and time) for both targets, as well as the median spectra of the target and reference stars.  
{\sha} shows a relative flat response with shows no obvious variations at the $\lesssim1$\% level.
{\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths. The periodic signal is coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.

{\bf [MORIS ANALYSIS FOR 1821?]}

@@

Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}. The uncertainties in these curves are {\bf [WHAT? HOW DETERMINED?]}. Again, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m.  These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -3~hr and +1~hr. In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr. As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and ignore these regions in our subsequent analysis.
{\bf [WE SHOULD VERIFY THIS]}

Each of the light curves were fit to a simple sinusoidal model:
\begin{equation}\label{eq:cosfit}
F(t) = A \cos(2 \pi (t - t_0)/\tau) + B t + C
\end{equation}
where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
For our initial fits, we allowed $A$, $t_0$, $B$ and $C$ to be free parameters, but fixed $\tau$ at the literature value of rotation period to mitigate systematic biases (e.g., convergence on a period of $\sim$24 hr). {\bf [IS THIS A PROBLEM IF YOU IGNORE TELLURIC BANDS? COULD YOU CONSTRAIN THE ALLOWED PERIOD RANGE (I.E., PRIOR). SHOULD DO A FIT WITH PERIOD FREE TO VARY TO GET A MEASURE OF THIS QUANTITY]}
We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.
{\bf [THIS IS LIKELY LEADING TO OUR "DETECTION" OF 0835; NEED ANOTHER WAY TO DO THIS]}.
We use the standard deviation of points near minimum to estimate the noise in the flux time series.
The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
